Two Resource one Predator

### 2018-07-04 1062_class/eco_model/HW/rk4/rk4.Rmd
up

@@

Download [rk4.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C10/rk4.c){target="_blank"}

@@

### R~1~ R~2~ Coexist
```c
double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8;
```

### R~1~ Exclude R~2~
```c
double a1=0.5, a2=0.5, b1=1.5, b2=1.0;
double r1=1.0, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R1_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' Exclude'*' R'[2]))
```

### R~2~ Exclude R~1~
```c
double a1=0.5, a2=0.3, b1=0.7, b2=1.1;
double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R2_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' Exclude'*' R'[2]))
```

>>>>

## R~1~, R~2~ Coexist
```c
double a1=0.7, a2=0.7, b1=1.0, b2=1.0;
double r1=0.8, r2=0.85, K1=1.2, K2=1.2, m=0.8;
```

## R~1~ Exclude R~2~
```c
double a1=0.5, a2=0.5, b1=1.5, b2=1.0;
double r1=1.0, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R1_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[1]*' Exclude'*' R'[2]))
```

## R~2~ Exclude R~1~
```c
double a1=0.5, a2=0.3, b1=0.7, b2=1.1;
double r1=0.7, r2=0.7, K1=1.2, K2=1.2, m=0.5;
```
```{r}
ggplot(R2_win)+
    geom_point(aes(x=time, y=R1, color="R1"), size=0.01)+
    geom_point(aes(x=time, y=R2, color="R2"), size=0.01)+
    geom_point(aes(x=time, y=Predator, color="Predator"), size=0.01)+
    guides(colour = 
            guide_legend(override.aes =
                             list(size=2)))+
    scale_x_continuous(
        breaks = seq(0,300,50))+
    labs(x="Time", y="Abundance",color="",
         title=expression('R'[2]*' Exclude'*' R'[1]))
```

@@

**Download [rk4.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C10/rk4.c){target="_blank"}**

@@
